{ \fontfamily{ptm}\selectfont Catalyst Meta Acceleration Framework: The history and the gist of it }

### 2024-11-28 Notebook LaTEX/Catalyst Accelerations/main.tex
>w<, changes

            \phi_0(x) &:= f(x_0) + \frac{A}{2}\Vert x - x_0\Vert^2, 

@@

@@

    \begin{lemma}[Lin's inexact proximal inequality]\label{lemma:lin-ixct-prox-ineq}
        Let $F$ be a $\mu\ge 0$ strongly convex and fix $\kappa$. 
        If $x_k$ is an inexact proximal point evaluation of $x_k \approx \mathcal J_{\kappa^{-1}} y_{k - 1}$ such that there exists $\epsilon_k$ where $\mathcal M^{\kappa^{-1}}(x_k; y_{k - 1}) - \mathcal M^{\kappa^{-1}}(\mathcal J_{\kappa^{-1}} y_{k - 1}, y_{k - 1}) \le \epsilon_k$. 
        Denote $x_k^* = \mathcal J_{\kappa^{-1}} y_{k - 1}$, then it has for all $x$: 
        \begin{align*}
            F(x) &\ge 
            F(x_k) + \kappa \langle y_{k - 1} - x_k, x - x_k\rangle
            + \frac{\mu}{2}\Vert x - x_k\Vert^2 
            + (\kappa + \mu)\langle  x_k - x_k^*, x - x_k\rangle 
            - \epsilon_k.
        \end{align*}
    \end{lemma}
    \begin{remark}
        For a detailed proof of the lemma, see 
        \hyperref[app:sec:inxct-pg-ineq]{Appendix\ref*{app:sec:inxct-pg-ineq}}.

    \end{remark}
    Using this inexact proximal inequality, we showed the proof of Lemma A.8 in Lin's paper \cite{lin_universal_2015} in 
    \hyperref[app:sec:appx-nes-est-seq]{Appendix \ref*{app:sec:appx-nes-est-seq}}
    and 
    \hyperref[app:sec:appx-nes-seq-errs-ctrl]{Appendix \ref*{app:sec:appx-nes-seq-errs-ctrl}}. 
    These result construct the Nesterov's estimating sequence by rolling up the error in the recurrence while avoiding intractable quantities appearing in the algorithm.

@@

            \widetilde{\mathcal J}_{L^{-1}} y_k

>>>>

            \phi_0(x) &:= F(x_0) + \frac{A}{2}\Vert x - x_0\Vert^2, 

@@

        We note that the smoothness conditions here are not involved in the definition of Guler's estimating sequence, or the function $F$. 

@@

    \begin{lemma}[Lin's inexact proximal inequality]\label{lemma:lin-ixct-prox-ineq}
        Let $F$ be a strongly convex with $\mu\ge 0$. 
        Let $\kappa$ be fixed. 
        If $x_k$ is an inexact proximal point evaluation of $x_k \approx \mathcal J_{\kappa^{-1}} y_{k - 1}$ such that there exists $\epsilon_k$ where $\mathcal M^{\kappa^{-1}}(x_k; y_{k - 1}) - \mathcal M^{\kappa^{-1}}(\mathcal J_{\kappa^{-1}} y_{k - 1}, y_{k - 1}) \le \epsilon_k$. 
        Denote $x_k^* = \mathcal J_{\kappa^{-1}} y_{k - 1}$, then it has for all $x$: 
        \begin{align*}
            F(x) &\ge 
            F(x_k) + \kappa \langle y_{k - 1} - x_k, x - x_k\rangle
            + \frac{\mu}{2}\Vert x - x_k\Vert^2 
            + (\kappa + \mu)\langle  x_k - x_k^*, x - x_k\rangle 
            - \epsilon_k.
        \end{align*}
    \end{lemma}
    \begin{remark}
        For a detailed proof of the lemma, see 
        \hyperref[app:sec:inxct-pg-ineq]{Appendix \ref*{app:sec:inxct-pg-ineq}}. 
        We note that it only uses the strong convexity of model function $\mathcal M^{\kappa^{-1}}(\cdot, y_{k - 1})$ (It's actually the quadratic growth condition around minimizer $x_k$ that is used in the proof), smoothness assumption of $F$ is not involved in here. 
    \end{remark}
    Using this inexact proximal inequality, we showed the proof of Lemma A.8 in Lin's paper \cite{lin_universal_2015} in 
    \hyperref[app:sec:appx-nes-est-seq]{Appendix \ref*{app:sec:appx-nes-est-seq}}
    and 
    \hyperref[app:sec:appx-nes-seq-errs-ctrl]{Appendix \ref*{app:sec:appx-nes-seq-errs-ctrl}}. 
    These result construct the Nesterov's estimating sequence by rolling up the error in the recurrence while avoiding intractable quantities appearing in the algorithm.

@@

            \widetilde{\mathcal J}_{L^{-1}} y_k, 
